Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-15 paper/paper.tex
Compare numerical and analytical solutions with LH1987
Comparing numerical and analytical results with phase

@@

\subsection{Unstable growth in infinite long-wave trains}
\label{subsection:unstable_growth}

>>>>

\begin{table}[h]
\label{table:modulation_literature_summary}
\caption{
  Summary of prior \cite{longuet1960changes,longuet1987propagation,zhang1990evolution} and present (this paper)
  approaches to calculating the modulation of short waves by long waves.
}
\begin{tabular}{cccccc}
\hline
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
\hline
L-HS (1960) & Velocity potential       & No  & No  & No  & Analytical \\
\hline
L-H (1987)  & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
ZM (1990)   & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes & No  & Analytical \\
            & conservation             &     &     &     & and numerical \\
\hline
\end{tabular}
\end{table}

@@

\subsection{Comparison with analytical solutions}
\label{subsection:comparison_with_analytical_solutions}

\begin{figure}[h]
\label{fig:numerical_solutions}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions of wavenumber, amplitude, and steepness modulation
  with their analytical solutions, for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_k}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_k.png}
\caption{}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_a}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_a.png}
\caption{}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_ak}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_ak.png}
\caption{}
\end{figure}

\subsection{Unstable growth in Pereux et al. (2021)}
\label{subsection:unstable_growth}
